ResultsNPS

### 2019-11-23 R/nps_reports/results.Rmd
added more datasets and now we show solving times for all instances.

Just like in the mean quality comparison, we compare among cases where all models found a **integer solution**.

@@

The following graph shows the solving times in seconds for each of the `r comparison_table %>% distinct(instance) %>% nrow` instances were an integer solution was found in all cases. If we reorder all models from fastest to slowest, we gain more insight on the distribution of solving times.

>>>>

Just like in the mean quality comparison, we compare among **all** cases.

@@

The following graph shows the solving times in seconds for each of the `r comparison_table %>% distinct(instance) %>% nrow` instances. If we reorder all models from fastest to slowest, we gain more insight on the distribution of solving times.
